\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-07 doc/sw-system.tex
Added agent probabilities plot, closes #36

>>>>

\Fref{fig:agent-probabilities} shows random selection of Agents' confusion
matrix elements, as they were on a particular day towards the end of the
CFHTLS project. Many volunteers classify  only a small number of images, and
so their Agents' confusion matrix elements remain close to their initial
values of (0.5,0.5). As more images are classified (shown by the yellow point
size), the Agents' matrix elements tend to move towards higher values, as the
volunteers attain greater skill levels (green point sizes, see
\Sref{sec:results} below) and the Agent learns more about them. In this
quadrant, the Agents perceive their volunteers to be ``astute.''

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW Agent confusion matrix elements. At a particular
snapshot, 200 random Agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as the Agents' volunteers view more images. Yellow point size is
proprtional to the number of images classified; green point size shows
Agent-perceived ``skill.''}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{Phil}{Include agent histories plot, discuss}

\todo{Phil}{Include subject trajectories plot, discuss}
